Et si l'on publiait la tendance-cycle ?

### 2025-10-20 Article/article.qmd
fichier renommé

  pdf:
    include-in-header: template/preambule.tex
    keep-tex: true
    classoption: french
    cite-method: biblatex
    pdf-engine: pdflatex
    fontsize: 12pt
    papersize: A4
    fig-width: 7.5
    fig-height: 3.5
    toc: false # to include abstract first
    fig-pos: 'H'
    geometry:
      - hmargin = 25mm
      - vmargin = 25mm
      # - top=2cm
      # - bottom=2.5cm
      # - left = 2.5cm
      # - right = 2.5cm
  # docx:
  #   number-sections: true
  #   fig-width: 6.3 # 16cm
  #   crossref:
  #     title-delim: "-"
crossref:
  tbl-prefix: table
  fig-prefix: figure
  sec-prefix: section
  eq-prefix: équation
execute: 
  cache: true
lang: fr
language:
 title-block-author-single: Auteur
echo: false
toc: true
number-sections: true
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: template/chicago-author-date.csl
author:
  - name: Alain QUARTIER-LA-TENTE 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
---

>>>>

  pdf:
    include-in-header: template/preambule.tex
    keep-tex: true
    classoption: french
    cite-method: biblatex
    pdf-engine: pdflatex
    fontsize: 12pt
    papersize: A4
    fig-width: 7.5
    fig-height: 3.5
    toc: false # to include abstract first
    fig-pos: 'H'
    output-file: "S14_ACTE_quartierlatente_JMS2025"
    geometry:
      - hmargin = 25mm
      - vmargin = 25mm
      # - top=2cm
      # - bottom=2.5cm
      # - left = 2.5cm
      # - right = 2.5cm
  # docx:
  #   number-sections: true
  #   fig-width: 6.3 # 16cm
  #   crossref:
  #     title-delim: "-"
crossref:
  tbl-prefix: table
  fig-prefix: figure
  sec-prefix: section
  eq-prefix: équation
execute: 
  cache: true
lang: fr
language:
 title-block-author-single: Auteur
echo: false
toc: true
number-sections: true
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: template/chicago-author-date.csl
author:
  - name: Alain QUARTIER-LA-TENTE 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
---
